\documentclass[10pt,a4paper]{article}

% Packages:
\usepackage[
    ignoreheadfoot, 
    top=1.8cm,
    bottom=1.8cm,
    left=1.8cm,
    right=1.8cm,
    footskip=1.0cm
]{geometry} % for adjusting page geometry
\usepackage{titlesec} % for customizing section titles
\usepackage{tabularx} % for making tables with fixed width columns
\usepackage{array} % tabularx requires this
\usepackage[dvipsnames]{xcolor} % for coloring text
\usepackage{enumitem} % for customizing lists
\usepackage{fontawesome5} % for using icons
\usepackage{amsmath} % for math
\usepackage[
    pdftitle={Erfan Habibi Ehsani's CV},
    pdfauthor={Erfan Habibi Ehsani},
    colorlinks=true,
    urlcolor=black
]{hyperref} % for links, metadata and bookmarks
\usepackage{lastpage} % for getting the total number of pages
\usepackage{changepage} % for one column entries (adjustwidth environment)
\usepackage{paracol} % for two and three column entries
\usepackage{needspace} % for avoiding page break right after the section title
\usepackage{iftex} % check if engine is pdflatex, xetex or luatex

% Font setup - New Times Roman
\usepackage{newtxtext,newtxmath} % Times New Roman font

% Some settings:
\raggedright
\AtBeginEnvironment{adjustwidth}{\partopsep0pt} % remove space before adjustwidth environment
\pagestyle{empty} % no header or footer
\setcounter{secnumdepth}{0} % no section numbering
\setlength{\parindent}{0pt} % no indentation
\setlength{\topskip}{0pt} % no top skip
\setlength{\columnsep}{0.15cm} % set column separation
\pagenumbering{gobble} % no page numbering

\titleformat{\section}{\needspace{4\baselineskip}\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule]

\titlespacing{\section}{
    -1pt
}{
    0.2cm  % Reduced space before section title
}{
    0.2cm
}

\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$} % custom bullet points
\setlist[itemize]{nosep, leftmargin=*, topsep=0.1cm, partopsep=0pt, parsep=0pt} % Compact lists

% Custom environments
\newenvironment{header}{\centering}{\par}
\newenvironment{onecolentry}{\begin{adjustwidth}{0pt}{0pt}}{\end{adjustwidth}}

% --- BEGIN DOCUMENT ---
\begin{document}

% Header
\begin{header}
    \fontsize{25pt}{25pt}\selectfont Erfan Habibi Ehsani 

    \vspace{4pt}

    \normalsize
    % Tehran, Iran
    % \kern 5.0pt\textbar\kern 5.0pt
    \href{mailto:erfan.habibi.ehsani@gmail.com}{erfan.habibi.ehsani@gmail.com} 
    \kern 5.0pt\textbar\kern 5.0pt
    \href{https://www.linkedin.com/in/erfanhabibi/}{linkedin.com/in/erfanhabibi} 
    \kern 5.0pt\textbar\kern 5.0pt
    \href{https://github.com/Erfanhabibi}{github.com/Erfanhabibi} 
    \kern 5.0pt\textbar\kern 5.0pt
    +98 914 497 5069 
\end{header}

% --- PROFESSIONAL SUMMARY ---
\begin{onecolentry}
\vspace{4pt}
\section{Professional Summary}
A driven and detail-oriented Computer Science student with a strong foundation in software engineering, machine learning, and system design. Proven ability to develop complex applications in Python and C\#/.NET, as demonstrated by advanced projects in network communication and message brokering. Seeking a challenging role to apply my skills in software development and problem-solving.
\end{onecolentry}


% --- EDUCATION SECTION ---
\section{Education}
\begin{tabularx}{\textwidth}{Xr}
    \textbf{B.Sc. in Mathematics and Computer Science}, Amirkabir University of Technology, Tehran, Iran  & \textit{2020 -- 2025 (Expected)} \\
\end{tabularx}
\textbf{Relevant Coursework:} Data Structures, Algorithms, Machine Learning, Advanced Programming 


% --- EXPERIENCE SECTION ---
\section{Experience}
\begin{tabularx}{\textwidth}{Xr}
    \textbf{C\# and .NET Bootcamp Trainee}, System Group (Hamkaran System), Tehran, Iran & \textit{2024} \\
\end{tabularx}
\begin{itemize}
    \item Developed and delivered multiple applications during an intensive one-month bootcamp focused on C\# and the .NET ecosystem.
    \item Applied object-oriented programming (OOP) principles and software development best practices to build robust, scalable applications.
    \item Collaborated in a team environment to complete practical projects, participating in code reviews and receiving mentorship from senior engineers.
\end{itemize}


% --- PROJECTS SECTION ---
\section{Projects}
\begin{tabularx}{\textwidth}{X@{\hskip 1em}r}
    \textbf{Message Broker System (C\#)} & \href{https://github.com/Erfanhabibi/MessageBroker}{github.com/Erfanhabibi/MessageBroker} \\
\end{tabularx}
\begin{itemize}
    \item Developed a robust Message Broker system in C\# to guarantee ordered, persistent, and reliable data transfer between distributed producers and consumers.
    \item Architected a decoupled plugin system using interfaces and attributes, allowing third-party developers to dynamically extend functionality.
    \item Implemented a multithreaded architecture allowing producers and consumers to define their thread counts, optimizing for concurrent performance.
    \item Engineered a file-based persistence layer to ensure message durability and prevent data loss during server failures or restarts.
    \item Built an automated retry mechanism and a configurable logging system to improve system resilience and monitorability.
\end{itemize}

\vspace{0.1cm}

\begin{tabularx}{\textwidth}{X@{\hskip 1em}r}
    \textbf{Server-Client Communication System (Python)} & \href{https://github.com/Erfanhabibi/python-socket}{github.com/Erfanhabibi/python-socket} \\
\end{tabularx}
\begin{itemize}
    \item Engineered a server-client system in Python for real-time image and audio data transfer using TCP/IP sockets.
    \item Developed a multi-threaded server with a Tkinter GUI to capture and manage incoming data streams from multiple clients.
    \item Utilized OpenCV for webcam image capture and PyAudio for audio recording, creating a robust multimedia streaming pipeline.
\end{itemize}


% --- SKILLS SECTION ---
\section{Skills}
\begin{tabularx}{\textwidth}{@{}lX@{}}
    \textbf{Programming Languages} & Python, C\#, C++, Java, C \\
    \textbf{Frameworks \& Platforms} & .NET, ASP.NET, Entity Framework, Django, Flutter \\
    \textbf{Machine Learning \& Data} & NumPy, pandas, scikit-learn, TensorFlow, Keras, SQL (MySQL, PostgreSQL) \\
    \textbf{Image Processing} & OpenCV, Pillow, scikit-image \\
    \textbf{Networking \& Security} & TCP/IP, Socket Programming, Network Security Fundamentals  \\
    \textbf{Tools \& Concepts} & Git, Linux Basics, Algorithms, Data Structures, Problem Solving \\
\end{tabularx}


\end{document}